---
title: "Assignment 2"
author: "Kholoud Alsadi"
date: "10/26/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

*Data summary of the data trees and the mean of the variable Girth.* 


```{r trees}
summary(trees)
mean(trees$Girth)
```

##  Plots:
**this a histogram that discribe the trees height and their frequancies.** 


```{r trees2, echo=FALSE}
hist(trees$Height)
```


# Omama
The boxplot for the Height variable is symmetric, while those for Girth and Volume are right skewed, and there is one outlier on the Volume boxplot.

```{r trees3, echo=FALSE}
par(mfrow=c(1, 3))
boxplot(trees$Girth, main="Girth")
boxplot(trees$Height, main="Height")
boxplot(trees$Volume, main="Volume")
par(mfrow=c(1, 1))
```

# Updated by Hanan

### Including scatter plots 

Scatter plots for all three variables are given below : 

```{r trees5, echo=FALSE}
par(mfrow=c(1,3))
attach(trees)
plot(Girth)
plot(Height)
plot(Volume)
```

The structure for the data can be found using the ' str ' function. There are 31 observations and 3 numerical variables.

```{r trees4, echo=FALSE}
str(trees)
```


